### 2016-11-01 methodsPaper/tex/materialsAndMethods.tex
Created two new figures
Also created appendix.Rnw to store old R code.
Added caption to DALYs figure (figure 3)
Added Disease Burden estimate equations.

The ITHIM model uses the comparative risk assesment framework to
estimate the population attributable fraction, $\af$.  In our case the
$\af$ represents the proportional change in national disease burden if
age and sex-specific active transport time means were changed.

@@

% \begin{figure}[t]
%   \centerline{\includegraphics[width=\textwidth]{./figures/fig2.pdf}}
%     \caption{}\label{fig1}
% \end{figure}

>>>>

As with the original ITHIM implementation we employed a comparative
risk analysis (CRA) across scenarios defined by mean active
transportation time, i.e., walking and cycling.

We compute the proportional change in national disease burden between
the baseline model and alternative scenarios, or population
attributable fraction, $\af$.  The population attributable fraction is
defined below, and computed for each disease included in the model,
namely Breast Cancer, Colon Cancer, Depression, Dementia, Diabetes and
Cardiovascular disease.

@@

\paragraph{Disease Burden Estimation}
\begin{equation}
B_1 = B_0(1-\af)\frac{\RR_1}{\sum_j \RR_j}
\end{equation}

$B_j = \gamma_jB_1$, where $\gamma_i = \frac{\RR_i}{\RR_1}$.  The
overall burden is then computed as the sum across quintiles,
$B=\sum B_j$.  Finally, $B_0$ is estimated from CDC data\ldots

\begin{figure}[t]
  \centerline{\includegraphics[width=\textwidth]{./figures/fig1}}
    \caption{}\label{fig1}
\end{figure}

\begin{figure}[t]
  \centerline{\includegraphics[width=\textwidth]{./figures/fig2.pdf}}
    \caption{}\label{fig2}
\end{figure}

\begin{figure}[t]
  \centerline{\includegraphics[width=\textwidth]{./figures/fig3.pdf}}
  \caption{Estimates for disease burden nationwide in terms of thousands of
    DALYs for each of the six diseases included in the model.
  }\label{fig3}
\end{figure}
